\sysfull

### 2018-04-15 paper/evaluation.tex
add figures to eval section

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/overallOverhead}
	\caption{ overall overhead breakdown: nc: No Coalecing, sc: Slow Coalescing, ea: Energy Aware coalescing \todo{}{Przemek}}
	\label{fig:overallOverheadBreakdown}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalEfficiency}
	\caption{ Coalescing algorithm efficiency:  nc: No Coalecing, sc: Slow Coalescing, ea: Energy Aware coalescing, eat: Energy \& Task Aware coalescing \todo{}{Przemek}}
	\label{fig:coalEfficiency}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/memAccess}
	\caption{ Memory access overhead breakdown:  nc: No Coalecing, sc: Slow Coalescing, ea: Energy Aware coalescing \todo{}{Przemek}}
	\label{fig:coalEfficiency}
\end{figure}
